---
title: "Homework #1 -- Pet Names Dataset"
author: "Sadeem Ghareeb Al Enazi\n"
date: "`r Sys.Date()`"
output: github_document
---

**Student ID:2201001438**

**Deadline:** 23:59 on Saturday, 13 February 2021

**Total Points:** 30


## Loading Packages

```{r load-packages, message = FALSE}

library(tidyverse)
library(openintro)
library(ggrepel)
```


##Exercises

`1.

(4 points)
```{r}

```
There are 52519 pets (same number of rows in dataset)



`2.

(4 points)

```{r}

```
There are 7 variables (license_issue_date-license_number-animal_name-species-primary_breed-secondary_breed-zip_code)


`3. Copy the code provided in the homework documentation and paste it here. 

(4 points)

```{r}
seattlepets %>%
count(animal_name, sort = TRUE)

```
The three most common pet names are: 

Name  frequency

---------------

Lucy  	439			
Charlie	387			
Luna  	355	



`4.

(10 points)

```{r species-name-top5, eval=TRUE}
seattlepets %>%
group_by(species) %>%
count(animal_name, sort = TRUE) %>%
  arrange(species,n)%>%
  slice_max(n, n = 5)
  


```
Actually what i noticed is : using slice_max(n, n = 5) after arrange it give me the same result regardless using arrange(species,n) or arrange(species,n) 

`5.  What names are more common for cats than dogs? The ones above the line or the ones below the line?


The ones below the line (Oliver and Lily)

(4 points)

`6. Is the relationship between the two variables (proportion of cats with a given name and proportion of dogs with a given name) positive or negative? What does this mean in context of the data?


It is a positive Correlation but NOT perfect because the frequency of dogs name is larger than cat names.



(4 points)